master thesis

### 2018-03-05 Paper - Latex/Paper - Skizze - v2.tex
pdf
Paper - Abstract - fix

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter*{Abstract}
  With increasing amounts of data, new investigations are also possible in phylogeny. This study 
    deals with the ancestral state reconstruction of parasitism in the tree of life of eukaryotes. 
    We predict unknown states of species and estimate origins and losses of parasitism. \\
  We performed an analysis of existing algorithms and selected a Sankoff maximum parsimony algorithm 
    using the R package \textit{Castor} \cite{Louca2017}. \\
  The challenge here is the size of the tree and the little information about it. \\
  Such a large phylogenetic tree does not completely exist and therefore we work with a synthesis 
    tree of OTL \cite{Hinchliff2015} which is highly multifurcated. \\
  For the 2,535,437 leaf nodes we could not gather much data. From the GloBI database 
    \cite{Poelen2014} whith we used for this, we could only collect 25,992 parasitic and 34,879 
    free-living species. It follows that we have only $\approx 2.4\%$ state information. \\

  Nevertheless, the analysis of our results revealed that our forecast is largely credible. \\
  We have compared the results of some subtrees with known knowledge (Chordata, Nematoda, 
    Platyhelminthes and Apicomplexa) and except for the Nematoda the results looked very good. In 
    the case of nematodes, the data situation is strongly shifted to the few parasites. \\
  Our number of origins we could partly compare with the results of Sara B. Weinstein and Armand M. 
  Kuris from their article \textit{Independent origins of parasitism in Animalia} \cite{Weinstein2016} 
    and have come to a similar magnitude. They identified 223 parasitic origins in Metazoa and we 
    were able to estimate about 300 origins. \\

>>>>

%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%---------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------- 
\chapter*{Abstract}
  With increasing amounts of data, new investigations are also possible in phylogeny. This study 
    deals with the ancestral state reconstruction of parasitism in the tree of life of eukaryotes. 
    We predict unknown states of species and estimate origins and losses of parasitism. \\
  We performed an analysis of existing algorithms and selected a Sankoff maximum parsimony algorithm 
    using the R package \textit{Castor} \cite{Louca2017}. \\
  The challenge here is the size of the tree and the little information about it. \\
  Such a large phylogenetic tree does not completely exist and therefore we work with a synthesis 
    tree of OTL \cite{Hinchliff2015} which is highly multifurcated. \\
  For the 2,535,437 leaf nodes we could not gather much data. From the GloBI database 
    \cite{Poelen2014} which we used, we could only collect 25,992 parasitic and 34,879 
    free-living species. It follows that we have only $\approx 2.4\%$ state information. \\

  Nevertheless, the analysis of our results revealed that our forecast is largely credible. \\
  We have compared the results of some subtrees with known knowledge (Chordata, Nematoda, 
    Platyhelminthes and Apicomplexa) and, except for the Nematoda, the results looked very good. In 
    the case of nematodes, the data situation is strongly shifted to the few parasites. \\
  We could partly compare our number of origins with the results of Sara B. Weinstein and Armand M. 
  Kuris from their article \textit{Independent origins of parasitism in Animalia} \cite{Weinstein2016} 
    and have come to a similar magnitude. They identified 223 parasitic origins in Metazoa and we 
    were able to estimate about 300 origins. \\
